%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author: Shubhankar Kamthankar
% Based on original template by Rahul Chauhan
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{rahulworld-resume}
\usepackage{}
% Add subtle horizontal spacing between columns
\setlength{\columnsep}{1.1cm}

% Compact vertical spacing for one-page fit
\setlength{\parskip}{2pt}
\setlength{\itemsep}{1pt}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.32\textwidth}
\begin{large}
	\headername{Shubhankar Kamthankar}\\
\end{large}
B.Tech + M.S in Computational Linguistics\\
CLD, IIIT Hyderabad \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links}
\noindent\rule{5cm}{0.4pt}

Github:// \href{https://github.com/So-bonkers}{\custombold{So-bonkers}} \\
LinkedIn:// \href{https://www.linkedin.com/in/shubhankar-kamthankar-8ab0501b5/}{\custombold{Shubhankar Kamthankar}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.4pt}
\subsection{OS}
GNU/Linux, Windows
\vspace{6pt}
\subsection{Languages}
C/C++, Python, TypeScript, BASH, R
\vspace{6pt}
\subsection{Frameworks}
Flask, Node.js, TensorFlow, PyTorch, scikit-learn, Keras, LangGraph
\vspace{6pt}
\subsection{Databases}
MySQL, Milvus, MongoDB
\vspace{6pt}
\subsection{Tools}
Git, Vim, Kaldi, SpeechBrain, Wavesurfer, Markdown

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\noindent\rule{5cm}{0.4pt}

Data Structures \& Algorithms\\
Linear Algebra, Discrete Mathematics\\
Advanced NLP, Speech Analysis\\
Speech-to-Speech Machine Translation\\
Operating Systems, Comp. Linguistics
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\noindent\rule{5cm}{0.4pt}\\

\datecolor{2020–2024}
\subsection{IIIT Hyderabad}
B.Tech + M.S in Computational Linguistics

\vspace{8pt}
\datecolor{2018–2020}
\subsection{KPC Junior College, Kharghar}
Percentage: 81.3\%

\vspace{8pt}
\datecolor{2017–2018}
\subsection{DAV International, Kharghar}
Percentage: 94.8\%

\end{minipage}
\hfill
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.64\textwidth}
\hspace*{0pt}\hfill IIIT Hyderabad, Gachibowli \\
\hspace*{0pt}\hfill Hyderabad – 500032 \\
\hspace*{0pt}\hfill Mob.: +91-9892512050 \\
\hspace*{0pt}\hfill Email: \textbf{\href{mailto:shubhankar.kam@gmail.com}{shubhankar.kam@gmail.com}} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\noindent\rule{12.5cm}{0.4pt}

\datecolor{Jun'25 – Present} \runsubsection{ML Engineer – Miko}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
\begin{itemize}
    \item Curated a multilingual child speech dataset of \textbf{641 hours} across languages, including \textbf{{\raise.17ex\hbox{$\scriptstyle\sim$}}500 hours of English child speech} — the largest openly available corpus of its kind.
    \item Trained a semantic VAD model based on \textit{smart-turn-v3.2} on proprietary child-speech data, achieving \textbf{96.2\% accuracy} vs.\ the baseline's 94.37\%.
\end{itemize}
\end{minipage}

\datecolor{Mar'25 – Jun'25} \runsubsection{ML Engineer Intern – MIVI}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Built an agentic framework for cab booking through Uber and Ola using speech recognition. Implemented in LangGraph and integrated into Mivi's marketing product, enabling interactive voice-based ride booking and increasing brand visibility.
\end{minipage}

\datecolor{Dec'23 – Oct'24} \runsubsection{DL Intern – Proxzar}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
\begin{itemize}
    \item Designed a reverse image search engine.
    \item Built a universal document converter using Docling for converting DOCX, PDF, PNG, XML, ASCIIDOC, and other formats to JSON for dataset generation and querying.
\end{itemize}
\end{minipage}

\datecolor{Jun'24 – Aug'24} \runsubsection{Core Researcher – Subtl.ai}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Developed a question-generation and recommendation feature for uploaded documents and integrated it with the existing API stack.
\end{minipage}

\datecolor{2022–2024} \runsubsection{Teaching Assistant ×4 – IIIT Hyderabad}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Assisted in courses: Language and Society, Introduction to Linguistics, Speech Analysis, and E-MSIT.
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\noindent\rule{12.5cm}{0.4pt}

\datecolor{2023–2024} \runsubsection{Stylr}
\descript{Python Dev, Computer Vision, Web Dev, ML}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Developed a fashion-apparel shopping app that recommends outfits based on users' wardrobes, featuring a Tinder-style interface. Built with MERN stack and hosted on Heroku. The Apparel Recognition Model (AppReMo) was trained on the Flipkart 500K dataset to detect apparel type and color.
\end{minipage}

\datecolor{2023–2024} \runsubsection{Digit Recognition}
\descript{Deep Learning, Speech Processing}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Created an ASR system to recognize spoken numerals in English and generate their Hindi textual and audio equivalents using a Machine Translation + TTS pipeline.
\end{minipage}

\datecolor{2020–2024} \runsubsection{Other Projects}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
\begin{itemize}
  \item \textbf{Canteen Portal:} MERN-based web app to track real-time canteen orders and transactions.
  \item \textbf{LSTM Blogs:} Authored a blog series analyzing RNNs, LSTMs, and sequence modeling performance.
  \item \textbf{C Shell / Xv6:} Implemented custom syscalls for process scheduling, I/O management, and networking.
  \item \textbf{Text Style Transfer:} Reproduced results from ``Text Detoxification using Large Pre-trained Neural Models.''
\end{itemize}
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}
\noindent\rule{12.5cm}{0.4pt}

\datecolor{2026 (Accepted)}\\
\textbf{Detecting Convolutional Codes Via a Markovian Statistic}\\
\textit{IEEE WCNC 2026 Conference} — Shubhankar Kamthankar, Guneesh Vats, Arti Yardi\\

\vspace{4pt}
\datecolor{2026 (4th Place)}\\
\textbf{Multi-Encoder Ensemble with Sequential BiLSTM Refinement for Style Change Detection}\\
\textit{PAN @ CLEF 2026} — Shubhankar Kamthankar, Arti Yardi\\

\end{minipage}
\end{document}
